# Using Quarto {#sec-more}

```{r setup}
#| include: false

library(tidyverse)
library(kableExtra)
theme_set(theme_bw())
```

Of course, the real reason to use Quarto is so you can embed R, python, Julia,
or other programmatic elements into your thesis.
Each `.qmd` file in your thesis is rendered as a separate R or Python section.
So any libraries you load, datasets you create, etc. in chunks will be available
for the rest of the chunks in this document, but not in subsequent documents.

## Figures in R
You can generate a figure with R, and refer to it in the text, such as I do with
@fig-example. By default, the code is shown in the HTML but not in the PDF. 

```{r fig-example}
#| label: fig-example
#| fig-cap: An example plot.
ggplot(mpg, aes(displ, hwy, colour = class)) + 
  geom_point() 
```


By default, the R figure will be centered in the text at 


## Tables in R
You can also create tables. I like using `kableExtra` and `modelsummary`. 
you can also refer to tables, like in @tbl-example. Note that table captions
are like titles, so should be in Title Case.

```{r tbl-example}
#| label: tbl-example
#| tbl-cap: Example Table.
mpg |> 
  group_by(manufacturer) |> 
  summarise(cty = mean(cty), hwy = mean(hwy)) |> 
  kbl(digits = 3, booktabs = TRUE) |> 
  kable_styling()
```




